### 2024-06-07 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

df_prevalence_species_mobilome <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\prevalence_comparisons-five_prevalent_species+EHMOS-metaphlan.csv)")

plot_df <- ggplot(df_prevalence_species_mobilome, aes(fill=SamplingSite, x=reorder(taxonomy,prevalency_percentage,sum,decreasing=T), y=prevalency_percentage))+  #'x=reorder(species,prevalency_percentage,sum,decreasing=T)' --> order stacked barplot with sum of values
  geom_bar(position = "dodge",stat = "identity",) +
  scale_fill_manual(values = c('Hospital-A'='#d93526','Hospital-B'='#f7a902','Hospital-C'='#1a6196'))+
  scale_x_discrete(labels=c('C. striatum','S. maltophilia','P. aeruginosa','K. pneumoniae','A. baumannii',
                            'E. anophelis','P. melaninogenica','P. oris','N. subflava','H. influenzae'))+
  theme_pubr(x.text.angle = 35)
plot_df

@@

### Fig s5g
bbone <- read_mauve_backbone(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\plasmids_publish_selected.backbone)',
                             ref=1, filter_low=0)
names <- c('NZ_CP010782.1',
           'Patient_6')
names(bbone$dna_segs) <- names

@@

### Fig s5g
bbone <- read_mauve_backbone(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\plasmids_selected-comparisons-NZ_CP045266.1.backbone)',
                             ref=1, filter_low=0)
names <- c('NZ_CP030131.1',
           'NZ_CP058229.1',
           'NZ_CP045266.1',
           'NZ_CP028795.1',
           'NZ_CP034127.1',
           'NZ_CP066522.1',
           'NZ_CP069175.1',
           'Patient_115')
names(bbone$dna_segs) <- names

@@

#replace patient name with patientID
df_plasmids_ani$query <- str_replace(df_plasmids_ani$query,'zhouboxun-xiangya','Patient_115')
colnames(df_plasmids_ani) <-  str_replace(colnames(df_plasmids_ani),'zhouboxun.xiangya','Patient_115')
#remove suffix: '.fasta' 
colnames(df_plasmids_ani) <- str_remove(colnames(df_plasmids_ani),'.fasta')
row.names(df_plasmids_ani) <- str_remove(df_plasmids_ani$query,'.fasta')

@@

@@

###  Fig 6c
ggviolin(df_instrain_comparison, "Group", "ANI",  fill = "Group",ylim=c(99.999,100),
         # palette = c("#fde5f0", "#bce3ed"),
         palette = c("#FFE4FA", "#A3C6DE"),
         add = "boxplot", add.params = list(fill = "white")) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=11,
                     vjust=.15,tip.length= c(0,0,0),label.y = 100) +
  scale_x_discrete(labels=c('Direct transmission','Indirect transmission'))+
  labs(x=NULL,y='Average nucleotide identity (%)',) +  
  theme_pubr(base_size = 26,legend ='none',x.text.angle = 30)

@@

>>>>

df_mge_abundance <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\mobile_elements_finder-stats_comparisons-mge_abundance.csv)")
my_comparisons <- list(c('prevalent','EHMOS'))

ggboxplot(df_mge_abundance, x="group", y="mge_num",
          color = "group", palette =c("#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00","#F781BF","#A65628","#F781BF"),
          add = "jitter",add.params = list(size = 1.5, alpha = 0.5))  +
  stat_boxplot(mapping = aes(color=group),geom = "errorbar",width=0.1)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=12,
                     vjust=.15,tip.length= c(0,0,0)) + 
scale_x_discrete(labels=c('More prevalent species','EHMOS'))+
  labs(x=NULL,y='Number of mobile elements',) +  
  theme_pubr(base_size = 36,legend ='none',x.text.angle = 30)

@@

### Fig s5g
bbone <- read_mauve_backbone(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\plasmids_selected-comparisons-NZ_CP010782.1.backbone)', # save in the same file 'plasmids_selected-comparisons.backbone'
                             ref=1, filter_low=0)
names <- c('NZ_CP010782.1',
           'Patient_6')
names(bbone$dna_segs) <- names

@@

### Fig s5g
bbone <- read_mauve_backbone(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\plasmids_selected-comparisons-NZ_CP045266.1.backbone)', # save in the same file 'plasmids_selected-comparisons.backbone'
                             ref=1, filter_low=0)
names <- c('NZ_CP030131.1',
           'NZ_CP058229.1',
           'NZ_CP045266.1',
           'NZ_CP028795.1',
           'NZ_CP034127.1',
           'NZ_CP066522.1',
           'NZ_CP069175.1',
           'Patient_115')
names(bbone$dna_segs) <- names

@@

#remove suffix: '.fasta' 
colnames(df_plasmids_ani) <- str_remove(colnames(df_plasmids_ani),'.fasta')
row.names(df_plasmids_ani) <- str_remove(df_plasmids_ani$query,'.fasta')

@@

### Figure 6
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

###  Fig 6c
###violinplot version (ANI as y-axis)
ggviolin(df_instrain_comparison, "Group", "ANI",  fill = "Group",ylim=c(99.999,100),
         # palette = c("#fde5f0", "#bce3ed"),
         palette = c("#FFE4FA", "#A3C6DE"),
         add = "boxplot", add.params = list(fill = "white")) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=11,
                     vjust=.15,tip.length= c(0,0,0),label.y = 100) +
  scale_x_discrete(labels=c('Direct transmission','Indirect transmission'))+
  labs(x=NULL,y='Average nucleotide identity (%)',) +  
  theme_pubr(base_size = 26,legend ='none',x.text.angle = 30)

@@

### Figure S6
### --------------------------------------------------------------------------------------------------------------------------------------------
